---
title: "First R Markdown file"
author: "Aubrey Pelletier"
date: "September 4, 2018"
output:
  html_document: 
    number_sections: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hello world!     What happens to funny spacing?             Is it preserved?

First line.   
Second line.  
Third Line.  

italic *this way*

boldface **like this**

subscript~lower~

superscript^raised^

strikethrough ~~for mistaks~~

#First level

##Second level

...

######Six level!


lists are easy

- first item
- second item
- third item, and yes it will keep everything aligned, just as it should be for longer text!
     - subitem
         - sub-subitem
      
      
>All musicians are subconciously mathematicians

The Thelonious Monk

Use single backtick for in-line emphasis `like this`.

Show literal text as `3 + pi`.

Start with r to get it to run r code like this `r 3 + pi`.

### Code fencing

```
#Comments are important!
pred <- seq(1,10) # make a vector of integers from 1 to 10
response <- runif(10)
print(response)

# now plot a graph
plot(x=pred, y=response, type="b")

```

```{r, eval=FALSE, echo=TRUE}
#Comments are important!
pred <- seq(1,10) # make a vector of integers from 1 to 10
response <- runif(10)
print(response)

# now plot a graph
plot(x=pred, y=response, type="b")

```

##Creating equations with `LaTex`

An `inline` equation is bracketed by single dollar signs $3 + 5 = 8$ like this.

For more complex equations, we will render them on a single line by using a double dollar sign to bracket them:

$$3 + 5 = 8$$

Keeps this as a stand-alone piece.

Subscripts as follows:

$$H_0 = Z_{a + b_{3z}}$$
