---
title: "Homework 7"
author: "Aubrey Pelletier"
date: "October 10, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---
#Creating Fake Data Sets to Explore Hypotheses

####I am using lizard sprint speed data from the internet that was used for one of previous homeworks I did. It has observations from each lizard, and their sprint speeds. I grabbed the mean and standard deviations from the excel document for the control group, and they had about 40 lizards, so I used that as my sample size to start. The data is attached below if curious. 
####Then, I created a hypothetical treatment to use, if I fed them, I hypothesized that they would run more slowly because they would be fat and slow, so I made my treatment data set have a lower mean, but the same standard deviation.

```{r}
read.table(file="15q24LizardSprintSpeed.csv")
```

```{r}
library(tidyverse)
 
nObs <- 40 #number of observations

LizSpeedControl <- rnorm(n=nObs, mean=2.14, sd=.44)
LizSpeedTreat <- rnorm(n=nObs, mean=1.98, sd=.44)

name <- ("Control")
name1 <- ("Treat") 
TreatCont <- rep(name, nObs)
TreatTreat <- rep(name1, nObs)
TreatVec <- c(TreatCont, TreatTreat)
print(TreatVec)

TreatVec <- c(rep(name, nObs), rep(name1, nObs)) #alternate code to get TreatVec
print(TreatVec)

Speeds <- c(LizSpeedControl, LizSpeedTreat)


ID <-seq_len(nObs)

LizData <- data.frame(ID,TreatVec,Speeds)
print(data)
str(data)

#Using ANOVA model because we have a categorical and continuous variable
ANOmodel <- aov(Speeds~TreatVec, data=LizData) #Speeds are a function of TreatVec(treatment)
print(ANOmodel)
print(summary(ANOmodel))

# Basic ggplot of ANOVA data

ANOPlot <- ggplot(data=LizData,
                  aes(x=TreatVec, y=Speeds,
                      fill = TreatVec)) +
  geom_boxplot()
print(ANOPlot)


```

###Step 5: Running the analysis switches frequently between significant and not significant, the p-value is very variable.
##Step 6, change the means to look for effect size (how small can the difference between 

```{r}
nObs <- 40 #number of observations

LizSpeedControl <- rnorm(n=nObs, mean=2.14, sd=.44)
LizSpeedTreat <- rnorm(n=nObs, mean=1.9, sd=.44)

name <- ("Control")
name1 <- ("Treat") 
TreatCont <- rep(name, nObs)
TreatTreat <- rep(name1, nObs)
TreatVec <- c(TreatCont, TreatTreat)
print(TreatVec)

TreatVec <- c(rep(name, nObs), rep(name1, nObs)) #alternate code to get TreatVec
print(TreatVec)

Speeds <- c(LizSpeedControl, LizSpeedTreat)


ID <-seq_len(nObs)

LizData <- data.frame(ID,TreatVec,Speeds)
print(data)
str(data)

#Using ANOVA model because we have a categorical and continuous variable
ANOmodel <- aov(Speeds~TreatVec, data=LizData) #Speeds are a function of TreatVec(treatment)
print(ANOmodel)
print(summary(ANOmodel))

# Basic ggplot of ANOVA data

ANOPlot <- ggplot(data=LizData,
                  aes(x=TreatVec, y=Speeds,
                      fill = TreatVec)) +
  geom_boxplot()
print(ANOPlot)
```

###6: Around 1.9 as the treatment value mean is when it starts becoming very variable between significant and non-significant results

#7: What is the minimum sample size you would need in order to detect a statistically significant effect?
####I lowered the mean of the treatment speeds to 1.8, because that was almost always significant, so that I could look separately at the sample size (nObs) to see where that came into play
```{r}
nObs <- 5 #number of observations

LizSpeedControl <- rnorm(n=nObs, mean=2.14, sd=.44)
LizSpeedTreat <- rnorm(n=nObs, mean=1.8, sd=.44)

name <- ("Control")
name1 <- ("Treat") 
TreatCont <- rep(name, nObs)
TreatTreat <- rep(name1, nObs)
TreatVec <- c(TreatCont, TreatTreat)
print(TreatVec)

TreatVec <- c(rep(name, nObs), rep(name1, nObs)) #alternate code to get TreatVec
print(TreatVec)

Speeds <- c(LizSpeedControl, LizSpeedTreat)


ID <-seq_len(nObs)

LizData <- data.frame(ID,TreatVec,Speeds)
print(data)
str(data)

#Using ANOVA model because we have a categorical and continuous variable
ANOmodel <- aov(Speeds~TreatVec, data=LizData) #Speeds are a function of TreatVec(treatment)
print(ANOmodel)
print(summary(ANOmodel))

# Basic ggplot of ANOVA data

ANOPlot <- ggplot(data=LizData,
                  aes(x=TreatVec, y=Speeds,
                      fill = TreatVec)) +
  geom_boxplot()
print(ANOPlot)
```

####At nObs=25 there starts to be some variation - the results are still significant a majority of the time, but not always. At n=10, it seems to be about 50-50, and at n=5, they don't seem to be significant most of the time