---
title: "Homework6"
author: "Aubrey Pelletier"
date: "October 3, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Long and Wide Data Formats
library(tidyverse)
data(iris)
print(iris)

longiris <- iris %>%
  gather(Sepal.Length:Petal.Width, key="Trait", value = 
           "Measurement") %>%
  arrange(Species)

print(longiris)


SpeciesTrait <- group_by(longiris, Species, Trait)
Averages <-summarize(SpeciesTrait, meanSepal.Length = mean(Measurement, na.rm = TRUE), number = n()) 
print(Averages)




#Simulating and Fitting Data Distributions

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

```{r}
#Read in random online data about lizard sprint speed: http://www.zoology.ubc.ca/~whitlock/ABD/teaching/datasets/15/datasets15.html
z <- read.table("15q24LizardSprintSpeed.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)

names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

#Maximum Liklihood parameters for Normal Distribution
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

#Normal Probability Density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

#Exponential Probability Density
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2

#Uniform Probability Density
 stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3

#Gamma Probability Density
 gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4

#Beta Probability Density
 pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

#Read in random online data about lizard sprint speed: http://www.zoology.ubc.ca/~whitlock/ABD/teaching/datasets/15/datasets15.html
z <- read.table("15q24LizardSprintSpeed.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)

names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

#Best Curve (Gamma) Maximum Liklihood parameters
print(gammaPars)
print(shapeML)
print(rateML)



gammaPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] 


#Simulate new data based on Maximum Liklihood parameters
set.seed(7)
LizardSprint <- (rgamma(68, shape = 24.37133, rate = 11.39317))
LizardS <- data.frame(1:68,LizardSprint)
names(LizardS) <- list("ID","myVar")

p2 <- ggplot(data=LizardS, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p2)

p2 <-  p2 +  geom_density(linetype="dotted",size=0.75)
p2

#Lizard Sprint Speed Original Data Plot
 p1
```

#Compare to simulated Data
 
###How do the two histogram profiles compare? Do you think the model is doing a good job of simulating realistic data that match your original measurements? Why or why not?
 
#####The two histograms are pretty similar - the plotted curves look pretty similar, but the simulated one is a bit less "normal" looking. Overall, I'd say the model did a pretty good job of simulating realistic data that matched the original measurements, but the left-hand tail in the original data is a bit larger than the simulated data. This looks like it is just due to chance in the simulated data however, because when I don't set the seed and run it multiple times, it generates curves with larger left-hand tails. The graphs also have similar densities, as represented by the y-values shown and the curves.
 