---
title: "Homework_4"
author: "Aubrey Pelletier"
date: "September 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
```{r}
x <- 1.1
a <- 2.2
b <- 3.3

z <- x^(a^b)
print(z)

z <- (x^a)^b
print(z)

z <- (3*x^3 + 2*x^2 +1)
print(z)
```
#2
```{r}
vec1 <- (seq(1:8))
vec2 <- (seq(from=7, to=1))
veca <- c(vec1, vec2)
print(veca)

vecx <- (seq(1:5))
vecb <- (rep(vecx, vecx))
print(vecb)

vec1 <- (seq(from=5,to=1))
vecc <- (rep(vec1, vecx))
print(vecc)
```
#3
```{r}
v3 <- runif(2)
names(v3) <- c("x", "y")
print(v3)

r <- sqrt(v3[1]^2 +v3[2]^2)
print(r)
theta <- atan(v3[2] / v3[1])

polar <-c(r, theta)
names(polar) <- c("r", "theta")
print(polar)
```
#4
```{r}
queue <- c("sheep", "fox", "owl", "ant")
print(queue)
queue1 <- c(queue, "serpent")
print(queue1)
queue2 <- queue1[2:5]
print(queue2)
queue3 <- c("donkey", queue2)
print(queue3)
queue4 <- (queue3[1:4])
print(queue4)
queue5 <- c(queue4[1:2], queue4[4])
print(queue5)
queue6 <- c(queue5[1:2], "aphid", queue5[3])
print(queue6)
#Where is the aphid in line?
Aphid <- which("aphid" == queue6)
print(Aphid)

#5, Create a vector of all integers from 1:100, not divisible by 2 ,3, or 7.
int <- (seq(1:100))
newint <- int[int%/%2!=0 & int%/%3!=0 & int%/%7!=0]
```
#6

```
Original Text: 
First String    Second      1.22      3.4
Second          More Text   1.555555  2.2220
Third           x           3         124

Command:
Find: \s{3,}
Replace: ,

Transformed text:
First String,Second,1.22,3.4
Second,More Text,1.555555,2.2220
Third,x,3,124

#7
Original
Ballif, Bryan, University of Vermont
Ellison, Aaron, Harvard Forest
Record, Sydne, Bryn Mawr

Find:
(\w+),\s(\w+),\s(.*)

Replace:
\2 \1 \(\3\)

Transformed Text:
Bryan Ballif (University of Vermont)
Aaron Ellison (Harvard Forest)
Sydne Record (Bryn Mawr)
